QuickSched: Task-based parallelism with dependencies and conflicts

### 2013-11-01 paper/paper.tex
new figures and backup.

The {\tt parent} field, which points to another resource, is
used to create hierarchical resources, i.e.~resources
that are themselves subsets of larger resources.
This can be useful, e.g.~in the context of particle simulations
described in the next section, where particles are sorted
into hierarchical cells which are used at different levels.

@@

The function {\tt qsched\_gettask} fetches a task from
one of the queues:
\begin{center}\begin{minipage}{0.9\textwidth}
    \begin{lstlisting}
struct task *qsched_gettask ( qsched *s , int qid ) {
  struct task *res = NULL;
  int k;
  while ( s->waiting ) {
    if ( ( res = queue_get( s->queues[qid] ) ) == NULL ) {
      loop over all other queues in random order with index k
        if ( ( res = queue_get( s->queues[k] ) ) != NULL )
          break;
      }
    else
      break;
    }
  if ( res != NULL ) {
    for ( k = 0 ; k < res->nr_locks ; k++ )
      res->locks[k]->owner = qid;
    for ( k = 0 ; k < res->nr_uses ; k++ )
      res->uses[k]->owner = qid;
    }
  return res;
  }
    \end{lstlisting}
\end{minipage}\end{center}
\noindent where the parameter {\tt qid} is the index of the
prefered queue.
If the queue is empty, or all of the tasks in that queue had
unresolved conflicts, the scheduler uses {\em work stealing}
\cite{ref:Blumofe1999}, i.e.~it loops over all other queues
in a random order (line~6) and tries to get a task from them
(line~7).
If a task could be obtained from any queue (line~13),
the resources it locks and uses are marked as now being owned
by the prefered queue (lines~14--17).
Finally, the task, or {\tt NULL} if no task could be obtained,
is returned.

@@

The main functions for setting up the scheduler are:
\begin{itemize}
    \item {\tt void qsched\_init( struct qsched *s , int nr\_queues , int flags )} \\
        Initializes a {\tt qsched} object with the given number of queues.
        The {\tt flags} parameter can be set to any bitwise or combination
        of {\tt qsched\_flag\_none},
        {\tt qsched\_flag\_yield}, and {\tt qsched\_flag\_pthread},
        which are described further below.
        This function must be called before any of the other
        functions are used.
        \vspace{1mm}
    \item {\tt void qsched\_free( struct qsched *s )} \\
        Releases all the memory and other resources allocated by the
        given {\tt qsched} object.
        After this function has been called, the {\tt qsched} will
        need to be re-initialized for reuse.
        \vspace{1mm}
    \item {\tt void qsched\_reset( struct qsched *s )} \\
        Clears the tasks and resources in the given {\tt qsched},
        but does not release the allocated memory or change
        the number of queues.
        \vspace{1mm}
    \item {\tt qsched\_task\_t qsched\_addtask( struct qsched *s , int type , unsigned int flags , void *data , int data\_size , int cost )} \\
        Creates a new task within the given {\tt qsched} and returns
        its handle.
        The {\tt type} and {\tt data} field are copied into the {\tt qsched}
        and passed to the execution function when the {\tt qsched} is run.
        The parameter flags is either {\tt task\_flag\_none} or
        {\tt task\_flag\_virtual}.
        Tasks marked as virtual do not have any action associated with them,
        e.g. they are used only to group or otherwise dependencies, and
        are not passed to the execution function in {\tt qsched\_run}.
        \vspace{1mm}
    \item {\tt qsched\_res\_t qsched\_addres( struct qsched *s , qsched\_res\_t parent )} \\
        Creates a new resource within the given {\tt qsched} and returns
        its handle.
        The {\tt parent} field is the handle of the heirarchical parent of
        the new resource or {\tt qsched\_res\_none} if the resource
        has no hierarchical parent.
        \vspace{1mm}
    \item {\tt void qsched\_addlock( struct qsched *s , qsched\_task\_t t , qsched\_res\_t res )} \\
        Append the resource {\tt res} to the task {\tt t}'s list of
        locks.
        The task {\tt t} will then conflict with any other task that
        also locks the resource {\tt res}, its hierarchical parents, or
        any resource hierarchically below it.
        \vspace{1mm}
    \item {\tt void qsched\_adduse( struct qsched *s , qsched\_task\_t t , qsched\_res\_t res )} \\
        Similar to {\tt qsched\_addlock}, yet the resource is only used and
        is not part of a conflict.
        This information is used when assinging tasks to specific queues.
        \vspace{1mm}
    \item {\tt void qsched\_addunlock( struct qsched *s , qsched\_task\_t ta , qsched\_task\_t tb )} \\
        Appends the task {\tt tb} to the list of tasks that the task {\tt ta}
        unlocks.
        The task {\tt tb} then depends on the task {\tt ta}.
        \vspace{1mm}
    \item {\tt void qsched\_run( struct qsched *s , int nr\_threads , qsched\_funtype fun )} \\
        Executes the tasks in the given {\tt qsched} using {\tt nr\_threads}
        threads via the execution function {\tt fun}, as described in the
        previous section.
        Once a {\tt qsched} has been initialized and filled with
        tasks and resources, it can be run more than once.
        \vspace{1mm}
\end{itemize}

@@

The source code of both examples is distributed with the
QuickSched library.

@@

@@

The Barnes-Hut tree-code is an algorithm to compute the
interactions between a set of particles

>>>>

The {\tt parent} field, which points to another resource, is
used to create hierarchical resources, i.e.~resources
that are themselves subsets of larger resources.
This can be useful, e.g.~in the context of particle simulations
described in the next section, where particles are sorted
into hierarchical cells which are used at different levels.
The owner field is the ID of the queue to which this
resource has been preferentially assigned.

@@

The function {\tt qsched\_gettask} fetches a task from
one of the queues:
\begin{center}\begin{minipage}{0.9\textwidth}
    \begin{lstlisting}
struct task *qsched_gettask ( qsched *s , int qid ) {
  struct task *res = NULL;
  int k;
  while ( s->waiting ) {
    if ( ( res = queue_get( s->queues[qid] ) ) == NULL ) {
      loop over all other queues in random order with index k
        if ( ( res = queue_get( s->queues[k] ) ) != NULL )
          break;
      }
    else
      break;
    }
  if ( res != NULL && s->reown ) {
    for ( k = 0 ; k < res->nr_locks ; k++ )
      res->locks[k]->owner = qid;
    for ( k = 0 ; k < res->nr_uses ; k++ )
      res->uses[k]->owner = qid;
    }
  return res;
  }
    \end{lstlisting}
\end{minipage}\end{center}
\noindent where the parameter {\tt qid} is the index of the
prefered queue.
If the queue is empty, or all of the tasks in that queue had
unresolved conflicts, the scheduler uses {\em work stealing}
\cite{ref:Blumofe1999}, i.e.~it loops over all other queues
in a random order (line~6) and tries to get a task from them
(line~7).
If a task could be obtained from any queue and task re-owning
is switched on (line~13),
the resources it locks and uses are marked as now being owned
by the prefered queue (lines~14--17).
Finally, the task, or {\tt NULL} if no task could be obtained,
is returned.

@@

The main functions for setting up the scheduler are:
\begin{itemize}
    \item {\tt void qsched\_init( struct qsched *s , int nr\_queues , int flags )} \\
        Initializes a {\tt qsched} object with the given number of queues.
        The {\tt flags} parameter can be set to any bitwise or combination
        of {\tt qsched\_flag\_none},
        {\tt qsched\_flag\_yield}, and {\tt qsched\_flag\_pthread},
        which are described further below.
        This function must be called before any of the other
        functions are used.
        \vspace{1mm}
    \item {\tt void qsched\_free( struct qsched *s )} \\
        Releases all the memory and other resources allocated by the
        given {\tt qsched} object.
        After this function has been called, the {\tt qsched} will
        need to be re-initialized for reuse.
        \vspace{1mm}
    \item {\tt void qsched\_reset( struct qsched *s )} \\
        Clears the tasks and resources in the given {\tt qsched},
        but does not release the allocated memory or change
        the number of queues.
        \vspace{1mm}
    \item {\tt qsched\_task\_t qsched\_addtask( struct qsched *s , int type , unsigned int flags , void *data , int data\_size , int cost )} \\
        Creates a new task within the given {\tt qsched} and returns
        its handle.
        The {\tt type} and {\tt data} field are copied into the {\tt qsched}
        and passed to the execution function when the {\tt qsched} is run.
        The parameter flags is either {\tt task\_flag\_none} or
        {\tt task\_flag\_virtual}.
        Tasks marked as virtual do not have any action associated with them,
        e.g. they are used only to group or otherwise dependencies, and
        are not passed to the execution function in {\tt qsched\_run}.
        \vspace{1mm}
    \item {\tt qsched\_res\_t qsched\_addres( struct qsched *s , int owner , qsched\_res\_t parent )} \\
        Creates a new resource within the given {\tt qsched} and returns
        its handle.
        The owner field is the initial queue ID to which this resource
        should be assigned, or {\tt qsched\_owner\_none}.
        The {\tt parent} field is the handle of the heirarchical parent of
        the new resource or {\tt qsched\_res\_none} if the resource
        has no hierarchical parent.
        \vspace{1mm}
    \item {\tt void qsched\_addlock( struct qsched *s , qsched\_task\_t t , qsched\_res\_t res )} \\
        Append the resource {\tt res} to the task {\tt t}'s list of
        locks.
        The task {\tt t} will then conflict with any other task that
        also locks the resource {\tt res}, its hierarchical parents, or
        any resource hierarchically below it.
        \vspace{1mm}
    \item {\tt void qsched\_adduse( struct qsched *s , qsched\_task\_t t , qsched\_res\_t res )} \\
        Similar to {\tt qsched\_addlock}, yet the resource is only used and
        is not part of a conflict.
        This information is used when assinging tasks to specific queues.
        \vspace{1mm}
    \item {\tt void qsched\_addunlock( struct qsched *s , qsched\_task\_t ta , qsched\_task\_t tb )} \\
        Appends the task {\tt tb} to the list of tasks that the task {\tt ta}
        unlocks.
        The task {\tt tb} then depends on the task {\tt ta}.
        \vspace{1mm}
    \item {\tt void qsched\_run( struct qsched *s , int nr\_threads , qsched\_funtype fun )} \\
        Executes the tasks in the given {\tt qsched} using {\tt nr\_threads}
        threads via the execution function {\tt fun}, as described in the
        previous section.
        Once a {\tt qsched} has been initialized and filled with
        tasks and resources, it can be run more than once.
        \vspace{1mm}
\end{itemize}

@@

The first test is the tiled QR decomposition originally
from \citeN{ref:Buttari2009}, which has been used as a benchmark
by other authors \cite{ref:Agullo2009b,ref:Badia2009,ref:Bosilca2012}.
This example only requires dependencies and is presented
only as a point of comparison to existing task-based
parallel infrastructures.

The second example is a Barnes-Hut tree-code, a problem
similar to the Fast Multipole Method described in both
\citeN{ref:Ltaief2012} and \citeN{ref:Agullo2013}.
This example shows how conflicts, modeled
via hierarchical resources, can be useful.

The source code of both examples is distributed with the
QuickSched library, along with scripts to run the benchmarks
and generate the plots used in the following.

@@

The QR decomposition was computed for a $2048\times 2048$
random matrix using tiles of size $64\times 64$ using QuickSched
as described above.
For the DGEQRF and DLARFT kernels, the respective routines
from the LAPACKE\footnote{\url{http://www.netlib.org/lapack/lapacke.html}}
library were used.
The DTSQRF and DSSRFT kernels were implemented by Sam Townsend
as part of his MSc thesis in Computer Science at Durham University.
For this matrix, a total of 11440 tasks with 32240 dependencies
were generated.

All tests were run on a 64-core AMD Opteron 6376 machine running
at 2.6\,GHz.
For these tests, OpenMP parallelism and resource re-owning
were used.
The QR decomposition was computed 10 times for each number of
cores, and the average thereof taken for the scaling and
efficiency results in \fig{QRResults}.
The timings are for {\tt qsched\_run}, including the cost of
{\tt qsched\_start}, which does not run in parallel.
Setting up the scheduler, tasks, and resources took, in all
cases, an average of 7.2\,ms.

\begin{figure}
    \centerline{\epsfig{file=figures/QR_scaling.pdf,width=0.9\textwidth}}
    \caption{Strong scaling and parallel efficiency of the tiled QR decomposition
        computed over a $2048\times 2048$ matrix with tiles of size
        $64\times 64$.
        The QR decomposition takes 233\,ms, achieving 73\% parallel
        efficiency, over all 64 cores.
        }
    \label{fig:QRResults}
\end{figure}

@@

The Barnes-Hut tree-code is an algorithm to approximate the
solution of an $N$-body problem, i.e.~computing all the
pairwise interactions between a set of $N$ particles,
in \oh{N\log N} operations, as opposed to the \oh{N^2}
naive direct computation.

The algorithm is based on a recursive octree decomposition:
Starting from a cubic cell containing all the particles,
the cell is recursivel bisected along all three spatial dimensions,
resulting in eight sub-cells, until the number of particles
per cell is smaller than some limit $n_\mathsf{max}$.

The particle interactions can also be formulated recursively:
Given a particle an a cell of particles, if the particle and cell
are sufficiently well separated, the particle-cell interactions
are approximated by interacting the particle with the cell's
centre of mass.
If the particle and the cell are too close, and the cell
has sub-cells, i.e.~it contained more than $n_\mathsf{max}$
particles and was split in the recursive octree decomposition,
then the particle is interacted with each of the sub-cells
recursively.
Finally, if the cell is not split, i.e.~it is a leaf cell
in the octree, then the particle is interacted with all
particles in the cell, except for the particle itself if
it is in the same cell.
This operation is performed for each particle, starting
with the root-level cell containing all the particles.

The cells have the following structure:
\begin{center}\begin{minipage}{0.9\textwidth}
    \begin{lstlisting}
struct cell {
  double loc[3], h[3], com[3], mass;
  int split, count;
  struct part *parts;
  struct cell *progeny[8];
  qsched_res_t res;
  qsched_task_t task_com;
  };
    \end{lstlisting}
\end{minipage}\end{center}
\noindent where {\tt loc} and {\tt h} are the location
and size of the cell, respectively.
The {\tt com} and {\tt mass} fields represent the cell's
center of mass, which will be used in the interactions.
The {\tt res} filed is the hieararchical resource representing
the cell's particles, and it is the parent resource of the cell
progeny's {\tt res}.
Similarly, the {\tt task\_com} is a task handle to
compute the center of mass of the cell's particles, and 
it depends on the {\tt task\_com} of all the progeny if
the cell is split.
{\tt parts} is a pointer to an array of {\tt count} 
particle strutures, which contain all the particle
data of the form:
\begin{center}\begin{minipage}{0.9\textwidth}
    \begin{lstlisting}
struct part {
  double x[3], a[3], mass;
  int id;
  };
    \end{lstlisting}
\end{minipage}\end{center}
\noindent i.e.~the particle position, accelleration, mass,
and ID, respectively.

The particle data is sorted hierarchically, following the
octree structure.
Unlike in many codes, where the leaves store an array of
pointers to the underlying particles, the cells, at all
levels, store only a pointer to the first of their own particles,
and the total number of particles.
The current approach, illustrated in \fig{CellParts} is not
only more compact, it also allows a direct and more cache-efficient access
to the list of particles for any inner node of the tree.
The cost of sorting the particles, with a recursive
partitioning similar to QuickSort \cite{ref:Hoare1962},
is in \oh{N\log N}.

\begin{figure}
    \centerline{\epsfig{file=figures/CellParts.pdf,width=0.9\textwidth}}
    \caption{Hierarchical ordering of the particle data structures
    (right) according to their cell (left).
    Each cell has a pointer to the first of its particles (same colour
    as cells) in the same global parts array.}
    \label{fig:CellParts}
\end{figure}

The task-based implementation will consist of four
types of tasks:
\begin{itemize}
    \item {\em Self}-interactions in which all particles
        in a single cell interact with all other particles in the
        same cell,
    \item {\em Particle-particle pair}-interactions in which
        all particles in a pair of cells interact with all
        particles in the opposite cell, and
    \item {\em Particle-cell pair}-interactions in which
        all particles in one cell are interacted with the
        center of mass of another cell.
    \item {\em Center of mass} tasks, which compute
        the center of mass of a single cell either from
        the sum of the centers of mass of its sub-cells
        if it has been split, or directly from the
        particles otherwise.
\end{itemize}

\begin{figure}
\begin{center}\begin{minipage}{0.9\textwidth}
    \begin{lstlisting}
enum { tSELF , tPAIR_PP , tPAIR_PC , tCOM };
void make_tasks ( struct qsched *s , struct cell *ci , struct cell *cj ) {
  int j, k;
  qsched_task_t tid;
  struct cell *data[2];
  if ( cj == NULL ) {
    if ( ci->split && ci->count > n_task )
      for ( j = 0 ; j < 8 ; j++ ) {
        make_tasks( s , ci->progeny[j] , NULL );
        for ( k = j+1 ; k < 8 ; k++ )
          make_tasks( s , ci->progeny[j] , ci->progeny[k] );
        }
    else {
      tid = qsched_addtask( s , tSELF , qsched_flags_none ,
        &ci , sizeof(struct cell *) , ci->count*ci->count );
      qsched_addlock( s , tid , ci->res );
      if ( ci->split )
        qsched_addunlock( s , ci->com , tid );
      }
    }
  else if ( ci and cj are well separated ) {
      data[0] = ci; data[1] = cj;
      tid = qsched_addtask( s , tPAIR_PC , qsched_flags_none ,
        data , sizeof(struct cell *)*2 , ci->count );
      qsched_addlock( s , tid , ci->res );
      qsched_addunlock( s , cj->com , tid );
      data[0] = cj; data[1] = ci;
      tid = qsched_addtask( s , tPAIR_PC , qsched_flags_none ,
        data , sizeof(struct cell *)*2 , cj->count );
      qsched_addlock( s , tid , cj->res );
      qsched_addunlock( s , ci->com , tid );
      }
  else if ( ci->split && cj->split && 
     ci->count*cj->count > n_task*n_task )
    for ( j = 0 ; j < 8 ; j++ )
      for ( k = 0 ; k < 8 ; k++ )
        make_tasks( s , ci->progeny[j] , cj->progeny[k] );
  else {
    data[0] = ci; data[1] = cj;
    tid = qsched_addtask( s , tPAIR_PP , qsched_flags_none ,
      data , sizeof(struct cell *)*2 , ci->count*cj->count );
    qsched_addlock( s , tid , ci->res );
    qsched_addlock( s , tid , cj->res );
    if ( ci->split && cj->split ) {
      qsched_addunlock( s , ci->com , tid );
      qsched_addunlock( s , cj->com , tid );
      }
    }
  }
    \end{lstlisting}
\end{minipage}\end{center}
    \caption{C-like pseudo-code for recursive task creation
        for the Barnes-Hut tree-code.}
    \label{fig:MakeTasks}
\end{figure}

These tasks can be created recursively over the cell hierarchy
as shown in the function {\tt make\_tasks} in \fig{MakeTasks}.
The function is called on the root cell with the root cell
and {\tt NULL} as its two cell parameters.
The function recurses as follows:
\begin{itemize}
    \item If called with a single (line~6), split (line~7) cell,
        recurse over all the cell's sub cells (line~9), and all
        pairs of the cell's sub cells (line~11),
    \item If called with a single unslplit cell (line~13),
        create a self-interaction task on that cell (line~14),
    \item If called with two cells that are sufficiently well
        separated (line~21), create two particle-cell pair
        interactions (lines~23 and~28) over both cells in
        opposite orders, which depend on the center of mass
        task of each cell,
    \item If called with two cells that are not well
        separated and both cells are split (line~33),
        recurse over all pairs of sub-cells spanning
        both cells (line~37), and
    \item If called with two cells that are not well separated
        and either of the cells are not split, create
        a particle-particle pair task over both cells.
\end{itemize}
\noindent where every interaction task additionally locks
the cells on which it operates (lines~16, 25, 30, and 42--43).

In order to reduce the number of tasks, and to prevent generating
too many very small tasks, the task generation only recurses
if the cells contain more than a minimum number $n_\mathsf{task}$
of threads each (lines~7 and~34).
The tasks themselves are then left to recurse over the sub-trees,
which is why in these cases, the tasks are made to depend on the
center of mass tasks (lines~17--18 and~41--47)
which may be used in the ensuing interactions.

\begin{figure}
\begin{center}\begin{minipage}{0.9\textwidth}
    \begin{lstlisting}
void comp_com ( struct cell *c ) {
  int j, k;
  c->com[0] = 0.0; c->com[1] = 0.0; c->com[2] = 0.0;
  c->mas = 0.0;
  if ( c->split )
    for ( k = 0 ; k < 8 ; k++ ) {
      struct cell *cp = c->progeny[k]
      for ( j = 0 ; j < 3 ; j++ ) c->com[j] += cp->com[j]*cp->mass;
      c->mass += cp->mass;
      }
  else
    for ( k = 0 ; k < 8 ; k++ ) {
      struct part *p = &c->parts[k];
      for ( j = 0 ; j < 3 ; j++ ) c->com[j] += p->x[j]*p->mass;
      c->mass += p->mass;
      }
  c->com[0] /= c->mass; c->com[1] /= c->mass; c->com[2] /= c->mass; 
  }

void comp_self ( struct cell *c ) {
  int j, k;
  if ( c->split )
    for ( j = 0 ; j < 8 ; j++ ) {
      comp_self( c->progeny[j] );
      for ( k = j+1 ; k < 8 ; k++ )
        comp_pair( c->progeny[j] , c->progeny[k] );
      }
  else
    for ( j = 0 ; j < c->count ; j++ )
      for ( k = j+1 ; k < c->count ; k++ )
        interact c->parts[j] and c->parts[k].
  }

void comp_pair ( struct cell *ci , struct cell *cj ) {
  int j, k;
  if ( ci and cj well separated ) {
    comp_pair_pc( ci , cj );
    comp_pair_pc( cj , ci );
    }
  else if ( ci->split && cj->split )
    for ( j = 0 ; j < 8 ; j++ )
      for ( k = 0 ; k < 8 ; k++ )
        comp_pair( ci->progeny[j] , cj->progeny[k] );
  else
    for ( j = 0 ; j < ci->count ; j++ )
      for ( k = 0 ; k < cj->count ; k++ )
        interact ci->parts[j] and cj->parts[k].
  }

void comp_pair_cp ( struct cell *ci , struct cell *cj ) {
  int k;
  for ( k = 0 ; k < ci->count ; k++ )
    interact ci->parts[k] and cj center of mass.
  }
    \end{lstlisting}
\end{minipage}\end{center}
    \caption{Task functions for the Barnes-Hut tree-code.}
    \label{fig:BHTasks}
\end{figure}

The functions for the task themselves are relatively
straight-forward and shown in \fig{BHTasks}, and the
execution function can be written as:
\begin{center}\begin{minipage}{0.9\textwidth}
    \begin{lstlisting}
void exec_fun ( int type , void *data ) {
  struct cell **cells = (struct cell **)data;
  switch ( type ) {
    case tSELF:
      comp_self( cells[0] );
      break;
    case tPAIR_PP:
      comp_pair( cells[0] , cells[1] );
      break;
    case tPAIR_PC:
      comp_pair_pc( cells[0] , cells[1] );
      break;
    case tCOM:
      comp_com( cells[0] );
      break;
    default:
      error( "Unknown task type." );
    }
  }
    \end{lstlisting}
\end{minipage}\end{center}

This Barnes-Hut tree-code was used to approximate the gravitational
N-Body problem for 1\,000\,000 particles with random coordinates the
parameters $n_\mathsf{max}=100$ and $n_\mathsf{task}=5000$.
Cell pairs were considered well separated if not adjecent.
Using the above scheme generated 161\,613 tasks, of which
512 self-interaction tasks, 18\,532 particle-particle interaction
task, 105\,120 particle-cell interaction tasks, and 37\,449
center of mass tasks.
Additionally 179\,632 dependencies were generated, along with
142'696 locks on 37\,449 resources.

As with the previous example, all
tests were run on a 64-core AMD Opteron 6376 machine running
at 2.6\,GHz.
For these tests, OpenMP parallelism was used and resource
re-owning was switched off.
The interactions  computed 10 times for each number of
cores, and the average thereof taken for the scaling and
efficiency results in \fig{BHResults}.
The timings are for {\tt qsched\_run}, including the cost of
{\tt qsched\_start}, which does not run in parallel.
Setting up the scheduler, tasks, and resources took, in all
cases, an average of 51.3\,ms.

\begin{figure}
    \centerline{\epsfig{file=figures/BH_scaling.pdf,width=0.9\textwidth}}
    \caption{Strong scaling and parallel efficiency of the Barnes-Hut tree-code
        computed over 1\,000\,000 particles.
        Solving the N-Body problem takes 3.5\,s, achieving 52\% parallel
        efficiency, over all 64 cores.
        }
    \label{fig:BHResults}
\end{figure}

Unlike the QR decomposition, the results scale well only to
32 cores, achieving 90\% parallel efficiency, and then
level off for increasing numbers of cores.
This, however, is not a problem of the task-based parallel
algorith, or of QuickSched, but of the cache hierarchies
of the underlying hardware.
On the AMD Opteron 6376, the cores are grouped into pairs
which each share a 2\,MB L2 cache.
Each group of four pairs, or eight cores, shares a common
6\,MB L3 cache.
It is the difference between the sum of the L2 caches and
the (smaller) L3 cache which causes problems.
